---
title: "NW_cleaning script"
output: html_notebook
---


```{r}
#Load packages
library(readxl)
library(writexl)
library(dplyr)
library(tidyverse)
library(dplyr)

survey_data <- read_excel("NGA2105_H_2022-03-16-09-30-15.xlsx",
                        sheet = 'NGA2105_HH_MSNA2022')
```
```{r}
#Survey time is too Afast <- survey_data %>%
cleaning_log <- survey_data%>%
  select(`_uuid`,"enumerator_id",`hh_count`,`end`,`start`) %>%
  filter(`hh_count` > 5 & `end` - `start`<= 20)%>%
  mutate(question_xml = "hh_count",question_name = "Time difference is too low",
  explanation = "The survey took less than 20 mins for HH with more than 5
  members-The enumerator need to be instructed to slow down.",old_value = "start_end", notes = "", new_value = "", reason = "") %>%
 select(`_uuid`,question_xml,question_name, explanation,"enumerator_id",notes, old_value, new_value, reason)
```


```{r}
#Income < #5000 but source of water is bottle water
  cleaning_log_1<- survey_data %>% 
 select(`_uuid`,"enumerator_id","main_source_water",
        "overall_income_estimate") %>%
  filter(`main_source_water` == "bottle_water" & `overall_income_estimate`
         == "less_than") %>%
  mutate(question_xml = "main_source_water", question_name = "What is the main 
  source of water used by your household for drinking?", explanation = 
           "HH has limited income but main source of water is bottle water", notes = "", 
         old_value = `main_source_water`, new_value = "", reason = "")%>%
  select(`_uuid`,question_xml, question_name, explanation, "enumerator_id", notes, old_value, new_value, reason) 

```
```{r}
#Income source is zero but reported other source of income.
  cleaning_log_2 <- survey_data %>% 
  select(`_uuid`,"enumerator_id","source_of_income",
         "overall_income_estimate") %>%
  filter(`overall_income_estimate` == 0 & `source_of_income` !=
           "no_income")%>%
mutate(question_xml = "source_of_income", question_name = "Over the
       course of the past 30 days, what were your household's primary 
       sources of income?", explanation =  "Household reported 0 income but 
       reported key sources of income. Please 
       check amount of income was correct.", notes = "", old_value = 
         `source_of_income`, new_value = "", reason = "")%>%
  select(`_uuid`,question_xml, question_name, explanation, "enumerator_id", notes, old_value, new_value, reason)

```
```{r}
#HH reported income but reported no income as key sources of income
  cleaning_log_3 <- survey_data %>% 
  select(`_uuid`,"enumerator_id","source_of_income",
         "overall_income_estimate") %>%
  filter(`overall_income_estimate` > 0 & `source_of_income` ==
           "no_income")%>%
mutate(question_xml = "info_hh_mem_y/ERL/source_of_income", question_name = "Over the
       course of the past 30 days, what were your household's primary 
       sources of income?", explanation =  "Household reported income but reported no 
       income as key sources of income. Please check amount of income was correct. ", notes = "", old_value = 
         `source_of_income`, new_value = "", reason = "")%>%
  select(`_uuid`,question_xml, question_name, explanation, "enumerator_id",
         notes, old_value, new_value, reason)
```
```{r}
# survey submitted after 3 days
  cleaning_log_4 <- survey_data %>%
    select(`_uuid`,"enumerator_id",`_submission_time`,
           `end`) %>%
    filter(`end` - `_submission_time` <= 4320)%>%
    mutate(question_xml = "start_end",question_name = "Survey submitted within 3 days", explanation =
             "Survey submutted after 3 days.", old_value = "", notes =
            "", new_value = "", reason = "") %>%
    select(`_uuid`,question_xml, question_name, explanation, "enumerator_id", notes, 
           old_value, new_value, reason)
```
```{r}
 #Survey duration is too long
  cleaning_log_5 <- survey_data %>%
  select(`_uuid`,"enumerator_id",`end`,`start`)%>%
  filter(`end` - `start` > 180)%>%
    mutate(question_xml = "start_end",question_name = "Survey took more than 3 hours.", explanation =
             "Survey was too long - please provide explanation ", old_value = "", notes =
             "", new_value = "", reason = "") %>%
    select(`_uuid`,question_xml, question_name, explanation, "enumerator_id", notes, 
           old_value, new_value, reason)
```
```{r}
# Household is likely to adopt coping strategies with a low income
  cleaning_log_6 <- survey_data %>%
    select(`_uuid`,"enumerator_id","overall_income_estimate","lack_income_cope")%>%
    filter(`overall_income_estimate` == "less_than", `lack_income_cope` == "none")%>%
    mutate(question_xml = "overall_income_estimate",question_name = "lack_income_cope", explanation = "This household is likely to adopt coping strategies with a low income. Please ask the enumerator to review their answers", old_value = "overall_income_estimate", notes = "", new_value = "", reason = "") %>%
    select(`_uuid`,question_xml, question_name, explanation, "enumerator_id", notes, 
           old_value, new_value, reason)
```
```{r}
#Shelter damage exits, enclosure issues should be reported accordingly
  cleaning_log_7 <- survey_data %>%
    select(`_uuid`,"enumerator_id","shelter_damages_defects","shelter_enclosure_issues")%>%
    filter(`shelter_damages_defects` == "yes" & "shelter_enclosure_issues" == "no")%>%
    mutate(question_xml = "Does the shelter currently have any damage or defects?",question_name =
             "shelter_damages_defects", explanation =
             "If shelter damage exits, enclosure issues should be reported accordingly", old_value = "", notes =
             "", new_value = "", reason = "") %>%
    select(`_uuid`,question_xml, question_name, explanation, "enumerator_id", notes, 
           old_value, new_value, reason)

```
```{r}
#Healthcare could be accessed within 15min, it shouldn't be considered as far away.
  cleaning_log_8 <- survey_data %>%
   select(`_uuid`,"enumerator_id", "nearest_health_care_children", "nearest_health_care_adult", 
           "nearest_health_care")%>%
    filter(`nearest_health_care_children` == "no_facility_nearby" | `nearest_health_care_adult`
           == "no_facility_nearby" & `nearest_health_care` == "less_than_15")%>%
    mutate(question_xml = "nearest_health_care_children",question_name =
             "nearest_health_care", explanation =
             "if healthcare could be accessed within 15min, it shouldn't be considered as far away.", old_value = "", notes =
             "", new_value = "", reason = "") %>%
    select(`_uuid`,question_xml, question_name, explanation, "enumerator_id", notes, 
           old_value, new_value, reason)
```
```{r}
#Household has been recently displaced, it should've experienced shocks or difficulties 
#in the past 6 months. Please check the shocks and difficulties experienced accordingly.
  cleaning_log_9 <- survey_data %>% 
    select(`_uuid`,"enumerator_id","diff_or_shocks", "year_first_displacement_recent")%>%
    filter(`diff_or_shocks`=="yes" & `year_first_displacement_recent`== "2021")%>%
    mutate(question_xml = "diff_or_shocks",question_name =
        "Did your household experience any difficulties or shocks over the course of the past 6 months?", explanation =
        "If the household has been recently displaced, it should've experienced shocks
        or difficulties in the past 6 months. Please check the shocks and difficulties 
        experienced accordingly.", old_value = "diff_or_shocks", notes =
        "", new_value = "", reason = "") %>%
    select(`_uuid`,question_xml, question_name, explanation, "enumerator_id", notes, 
           old_value, new_value, reason)
```
```{r}
#Household has no source of electricity, it shouldn't have access to hours of electricity.
  cleaning_log_10 <- survey_data %>%
    select(`_uuid`,"enumerator_id","main_source_electricity", "hours_of_electricity")%>%
    filter(`main_source_electricity` == "no_source" & `hours_of_electricity` != "no_access")%>%
    mutate(question_xml = "What is your household main source of electricity?",question_name =
    "main_source_electricity", explanation =
    "If household has no source of electricity, it shouldn't have access 
    to hours of electricity. Please indicate why so and check if the hours 
    of electricity is a typo.", old_value = "main_source_electricity", notes =
             "", new_value = "", reason = "") %>%
    select(`_uuid`,question_xml, question_name, explanation, "enumerator_id", notes, 
           old_value, new_value, reason)
```
```{r}
#Checking expenditures (expenditure_shelter_repair, expenditure_non_food_items...) 
#cannot be equal or more to 1 and less than 1000
cleaning_log_11 <- survey_data %>%
select(`_uuid`,"enumerator_id", "expenditure_shelter_repair",
       "expenditure_non_food_items",
       "expenditure_health_related",
       "expenditure_education_related",
       "expenditure_debt_related",
       "expenditure_other_needs")%>%
  filter(`expenditure_shelter_repair`+  
         `expenditure_non_food_items` +  
          `expenditure_health_related`+ 
       `expenditure_education_related`+  
         `expenditure_debt_related`   +  
         `expenditure_other_needs`    < 1000)%>%
  mutate(question_xml = "During the past 6 months, how much did your household spend,
         in local currency, on each of the following categories of items 
         for domestic consumption? For each, please estimate the total 
         amount spent by your household using all modalities (cash, credit,
         mobile money, etc.)",question_name =
           "expenditure_past_6_months", explanation =
        "expenditures (expenditure_shelter_repair,
        expenditure_non_food_items...) cannot be equal
        or more to 1 and less than 1000;", old_value = "expenditure_past_6_months", notes =
           "", new_value = "", reason = "") %>%
  select(`_uuid`,question_xml, question_name, explanation, "enumerator_id", notes, 
         old_value, new_value, reason)
```
```{r}
#Checking amount of debt
cleaning_log_12 <- survey_data %>%
  select(`_uuid`,"enumerator_id","amount_of_debt")%>%
  filter(`amount_of_debt` < 1000)%>%
  mutate(question_xml = "What is your household's current total
     amount of debt, in local currency?",question_name =
    "amount_of_debt", explanation =
    "Amount_of_debt cannot be less than 1000, but more than 0",
    old_value = "amount_of_debt", notes =
    "", new_value = "", reason = "") %>%
  select(`_uuid`,question_xml, question_name, explanation, "enumerator_id", notes, 
         old_value, new_value, reason)
```
```{r}
#hh_count is between 1 and 5 and water_used_day is less than 10
cleaning_log_13 <- survey_data%>%
  select(`_uuid`,"enumerator_id",`hh_count`,"water_used_day") %>%
  filter(`hh_count` < 5 & "water_used_day" < 10)%>%
  mutate(question_xml = "How many liters of water do you and your household 
    approximately use in a day for all  purposes?",question_name =
     "water_used_day", explanation =
    "hh_count is between 1 and 5 and water_used_day is less than 10",
    old_value = "water_used_day", notes =
    "", new_value = "", reason = "") %>%
  select(`_uuid`,question_xml, question_name, explanation, "enumerator_id", notes, 
         old_value, new_value, reason)
    
```
```{r}
 summary_issues = rbind(cleaning_log,cleaning_log_1,cleaning_log_2,cleaning_log_3,
                         cleaning_log_4, cleaning_log_5,
                         cleaning_log_6, cleaning_log_7, cleaning_log_8, cleaning_log_9,
                         cleaning_log_10, cleaning_log_11, cleaning_log_12,cleaning_log_13)
write_xlsx(summary_issues, "flagged_data_1.xlsx")

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
